Linking microbial communities to ecosystem functions: what we can learn from genotype-phenotype mapping in organisms

### 2019-07-16 manuscript/main.tex
Update manuscript text

\section*{Tasks} 
\begin{enumerate}
\item What is novel about this? The first anyone has treated an ecosystem like an
organism. The first time anyone has done this correlative approach well
by considering environmental and spatial structure in the data. 
\item Interpret model output
\item Decide whether to include Gabon data, Brazil data, or both
\end{enumerate}

@@

Microorganisms mediate many biogeochemical processes and yet the link between
microbial biodiversity and ecosystem function remains unknown. 
Ecologists have investigated the effects of changing
biodiversity on ecosystem function for decades, but this research has primarily
focused on linking terrestrial plant community richness with productivity
\citep{hooper2005}. More recently, there has been an interest in linking
microbial community composition to ecosystem functions such as host disease 
and soil greenhouse gas emissions \citep{schimel1998, singh2010}. 
However, it remains unclear to what extent 
microbial community composition is important for determining the rates of ecosystem-scale
functions.  This uncertainty limits our ability to predict and manage host
health and global biogeochemical cycles. To
address this challenge, we propose integrating traditional
biodiversity-ecosystem function research with ideas from genotype-phenotype
mapping in population genetics. This connection will help determine
whether microbial community
composition alters ecosystem-scale functions independent
of the underlying environmental variation.

If local selection always optimizes the available biodiversity to maximize
ecosystem function, them microbial community composition should not matter for
pedicting the rates of microbially-mediated functions. Instead, 
the rates of these functions should be determined by the
underlying environmental variation. In this case, the microbial community simply
acts as a conduit through which the abiotic
environment alters ecosystem function. However, experiments that manipulate the
connection between environmental factors and microbial community composition
such as environmental treatments, common gardens, and reciprocal transplants
have shown different rates of ecosystem functions for different microbial
communities. This has been observed for plant decomposition
\citep{strickland2009}, plant phenology \citep{panke-buisse2015}, soil nitrogen
cycling \citep{balser2005}, and soil greenhouse gas emissions
\citep{cavigelli2000}. Therefore, variation in microbial community composition
seems to generate variation in ecosystem function. However, in order to
incorporate microorganisms into ecosystem models, we need to identify what
aspects of microbial biodiversity are associated with variation in ecosystem
function.

Most studies of microbial community function focus on one of two aspects of
microbial community structure that are hypothesized to be predictive of
ecosystem function. The first aspect is functional gene or transcript abundance.
In this case, qPCR or shotgun metagonemic sequencing is used to target a gene
or transcript that is a putative marker for a microbial process. For example,
the gene \textit{mcrA}, which encodes the enzyme that performs the final step in
methanogenesis, is hypothesized to be correlated with the rate of
methane production. Other examples include \textit{pmoA} and methanotrophy,
\textit{nifH} and nitrification, and \textit{nosZ} and denitrification. The
rationale for this hypothesis is that the abundance of a functional group (as
inferred from marker gene abundance) should correspond to the rate of the
process performed by that group. There are examples where this relationship
holds \citep{freitag2009, freitag2010, schnyder2018}. However, a review of these
studies found that the abundance of a functional gene or transcript is rarely
correlated with the rate of the corresponding process, with most effects either
negative or not significant \citep{rocca2015}.

The second aspect of microbial community structure hypothesized to predict
ecosystem function is taxonomic or functional
diversity. Diversity is either estimated using a measure of community
composition such as 16S rRNA gene ribotyping or manipulated through some proxy
of diversity such as sequential dilution or varying filter sizes. Studies that
experimentally manipulate diversity generally find a relationship between
the applied diversity treatment and ecosystem functions including methanotrophy
\citep{schnyder2018}, phosphorus leaching, greenhouse gas emissions
\citep{wagg2014}, and decomposition \citep{maron2018}. However, in each of these
cases, richness is confounded with other factors such as presence or absence of
major phylogenetic groups (nematodes, fungi) or abundance of microbial cells. In
addition, assembled microbial communities pose the same challenges as
macroorganismal diversity experiments, for example no replication at the highest
diversity treatment. A review of microbial diversity studies shows that
microbial community taxonomic and functional diversity add little variance
explained to models of ecosystem function. Overall, functional gene
abundance and community diversity improve models of ecosystem function less than
one third of the time and increase variance explained by an average of only 8 percentage
points \citep{graham2016}.

These approaches follow on the tradition of macroorganismal
biodiversity-ecosystem function research by measuring or manipulating diversity
and comparing it to function or by looking at the association between richness
or abundance of a functional group (e.g. plants) and the function performed by
that group (e.g. productivity). However, in the case of microbes, our knowledge
of functional groups is quite limited. We cannot be sure that we're accurately
estimating the abundance or diversity of soil microbial functional groups the
way we can plants in a grassland.

Organisms exhibit population differentiation due to geographic and ecological
processes \citep{wright1943}. Neutral processes such as local genetic drift and
reduced gene flow due to geographic separation can lead to population
differentiation. In addition, environmental distance can lead to selection
against migrants \citep{hendry2004} and local selection on endemic populations
to generate variation. Microorganisms also exhibit biogeographic patterns due to
ecological selection and geographic separation \citep{martiny2006}. If dispersal
is non-limiting then the most productive species should always be present and
composition should not matter for local ecosystem function. However, if important
functional groups are dispersal-limited, lost to drift, or are unable to
colonize a site, then there could be important functional consequences of
community differentiation to geographic or ecological isolation.

@@

The challenge of mapping microbial community structure to ecosystem function is
analogous to the challenge of identifying the genetic basis of complex traits in
organismal populations. In the latter case, a population exhibits variation in a
phenotype (e.g. height or disease state) as well as variation in potentially
thousands of genetic loci (usually identified as single nucleotide polymorphisms
(SNPs)). To identify the genetic basis for a trait, investigators sample from
this population and correlate phenotype with genotype. In most cases, there are
many more loci than individuals and we do not know the function of genes
associated with these SNPs. Genetic markers identified in these genome-wide association
studies can be the target for future research to dissect the function of those
genes, can be added or removed to test their association with the trait, or can
be used as marker for that disease or phenotype even if it has no known
mechanistic association. This mirrors the problem of microbial
structure-function mapping. In this case, a population of hosts or ecosystems exhibit
variation in a particular trait or ecosystem function putatively mediated by
microorganisms as well as variation in metagenomic composition. Investigators
could sample from this population of ecosystems and correlate the rate of an
ecosystem function with microbial community composition or gene composition.

Population geneticists trying to make robust associations between genetic loci
and phenotype must take into account population stratification. Population
stratification due to shared ancestry or local selection can lead to spurious
associations between genes and traits. For example, human height varies
across Europe in a latitudinal gradient. Positive associations between genes and
phenotypes can arise because of true associations, through linkage
disequilibrium with true genes, or through admixture \citep{lander1994}.
Microbial structure-function connections could pose these same problems. There
could be true associations between a microorganism and the ecosystem function
performed by that taxon, or there could be systematic
co-occurrence patterns between one taxon and a causal taxon like metabolic
networks, or there could be admixture due to shared history or selection within
a subset of ecosystems. This is true for ASVs in ribotyping 16S datasets and for
genes in metagenomic (or other -omic) datsets. 
Robust structure-function associations rely on
controlling for these factors.

\section{Methods}

@@

After determining which variance components were significant, we tested the
effect of each ASV on the rate of ecosystem function. We fit a variance
component model for each ASV with ASV abundance as the fixed effect and random
effects for each of the variance components. This tests the relationship between
taxon abundance and the rate of ecosystem function after controlling for
population stratification and data structure. Significant ASVs were identified
by controlling the false discovery rate

@@

@@

In this paper, we argue that the traditional approach to microbial BEF research
ignores important understandings about the nature of ecological processes in
determining the distribution of microorganisms. The marker gene hypothesis has
proven unsuccesful in predicting the rates of ecosystem functions from the
abundance of functional genes and in our example study was not significant in one case and
was significant in another, though explained a small amount of the variation.
Similarly, diversity metrics from the entire Prokrayotic community were not
explanatory. These results agree with recent reviews of this literature and
demonstrate that these approaches are not a fruitful avenue for elucidating
microbial structure-function connections.

Instead, microbial ecologists should treat microbial communities as analogous to
organisms with the metagenome representing the community genome. In this case,
ecosystem function represents a phenotype at the community level. As in
organismal biology, this ecosystem phenotype will be a mix of genotypic effects and
environmental effects. Using this conceptual framework, population genetic
approaches can be applied to microbial community datasets to identify

Treating ecosystems like organisms. Calculating community heritability. Possible
approaches: variance component modeling, experimental ecosystem
selection/experimental evolution, CAFE and the Price equation. Need to collect
data in such a way to optimally use these techniques that already exist.

@@

\section*{Old Text}

\subsection{Biodiversity increases ecosystem function in macrobial communities}

Local species richness is correlated with ecosystem function
\citep{hooper2005}. Most BEF research has focused on terrestrial plant 
communities where species losses lead to decreases in community abundance or biomass
\citep{naeem2003}. There are
two major explanations for this phenomenon. The first is the sampling effect
where a more diverse community is more likely to have one particularly
productive species \citep{cardinale2006}. The second is niche complementarity where more species are
more likely to occupy separate niches within the same ecosystem resulting in
more efficient resource use and greater biomass.

Regional species diversity may also be important for
local ecosystem functioning when metacommunity dynamics regulate the
diversity and composition of communities \citep{leibold2017}. 
Typical BEF research focuses on local selection
as a driver of ecosystem function. However, if regional
diversity is important, then dispersal processes could alter local species diversity and composition resulting in
a change in ecosystem function. This model is referred to as Community Assembly
and the Functioning of Ecosystems (CAFE). Community assembly can alter ecosystem
function if limiting dispersal reduces the likelihood of a highly productive
species from dispersing to a local site or if high dispersal of an unproductive
species overwhelms local selection.

The CAFE approach has been demonstrated using the Price equation where a change in ecosystem function between two, matched
observations can be attributed to species additions, species losses, and
changes in abundance of shared species \citep{fox2006,
bannar-martin2018}. To
calculate these vectors, function must be attributed at the species level (e.g.
biomass measurements of individual plant species). The CAFE framework demonstrates
that not only local richness, 
but also the composition of communities is important to the functioning of ecosystems.

\subsection{Current approaches to microbial BEF reveal little about 
structure-function mapping}

The trajectory of microbial BEF research has differed from that of macrobial BEF
for three reasons. First, microbial communities are
immensely complex with orders of magnitude more taxa than macrobial communities
and great intra-taxon variation for certain traits. Second, the way we measure
microbes using marker gene sequences does not allow us to attribute portions of
a function of interest to individual taxonomic groups . We can only
measure function in aggregate across an entire community. Finally, we cannot be
sure that the taxonomic groups that putatively perform a function are the ones
contributing in this moment.

As a result of these limitations, microbial ecologists have taken a different
approach to assessing BEF relationships for microbial communities than others
have for macrobial communities. This is generally a correlative approach where
certain community attributes that can be derived from a community matrix are
tested in terms of their relationship with function. These approaches make
different assumptions about how microbial communities should map onto function.
On one end of the spectrum, it is hypothesized that functional gene abundance - genes that
code for an enzyme that performs one step of a process - should be correlated
with the rate of the process associated with that gene. In this case, qPCR
is used to quantify the abundance of a functional gene to test whether it is
correlated with the rate of a process. This approach has had varied success and even the abundance of a
functional gene that putatively performs a process is rarely correlated with
that process \citep{rocca2015}. On the other end of the
spectrum, investigators make few assumptions about which members of the community should
alter function and so compute
taxonomic richness or other diversity metrics from the entire Prokaryotic
community inferred from 16S rRNA gene sequences. Taxonomic or functional
diversity of the Prokaryote community generally adds little variance explained
to models of ecosystem function \citep{graham2016}.

\subsection{Biology through analogy: structure-function mapping is similar
to genotype-phenotype mapping}

The challenges described above for mapping microbial community structure to
ecosystem function are analogous to the problem of identifying the
genetic basis of complex traits in organismal populations. In that case,
each individual organism has a level for a phenotype (e.g. presence
or absence of a disease state) as well as a vector of potentially
thousands of genetic loci with different alleles or single nucleotide
polymorphisms (SNPs). To identify the genetic basis for this trait, we sample
a population of organisms and try to correlate a matrix of SNPs with a
vector of phenotypes. In most cases, there are many more loci than
individuals, we cannot directly attribute a phenotypic state to a particular
SNP, and we do not know the function of genes associated with these
SNPs. This mirrors the problem of microbial structure-function mapping
and presents a potential set of analyses that could be applied in
microbial ecology.

In addition to the nature of the data, population geneticists have other
considerations when trying to make robust associations between phenotype
and SNPs. For example, loci within the genome that are close together tend
not to assort independently due to linkage disequilibrium. In addition,
organisms exhibit population stratification due to a variety of historical
and selective effects. For example, shared ancestry among European
populations of humans results in an association between genotype and
geography across Europe \citep{novembre2008}. This population structure
can lead to false positives when trying to correlate human genotypes
with genetic diseases or other phenotypes such as height (citation).

In general, organisms exhibit population differentiation due to spatial
and environmental patterns \citep{wright1943}. For geography, local genetic
drift and reduced gene flow due to geographic separation can lead to population
differentiation \citep{wright1943}. In addition, environmental distance can lead to both selection
against migrants \citep{hendry2004} and local selection on endemic populations to
generate variation. While
these processes have primarily been described for macrobial populations, the
same principles apply to microorganisms and should be considered
in microbial structure-function mapping \citep{martiny2006}.

\subsection{Reframing the question: Is variation in microbial community
structure associated with differences in ecosystem function across space,
time, and environments?}

Typical microbial ecosystem function research focuses on whether microbial
community composition is important at the ecosystem level
\citep{schimel1998, cavigelli2000, balser2005, graham2016}. Given that
microbial functional groups typically mediate biogeochemical processes
and so the loss of a functional group will certainly alter function,
the answer is "yes". However, this question does not address whether
microbial community variation is actually useful for predicting or 
managing ecosystem functions. To address that problem, we need to know
whether variation within a functional group matters to variation in
ecosystem function. If local selection always optimizes the available
biodiversity to maximize process rates given the underlying environmental
variation, then composition should not matter, because we should be able
to predict ecosystem function from abiotic factors alone. Environmental
treatments, common gardens, and reciprocal transplants have shown
different functional potential for different community compositions.
In addition, spatial patterns for microbial communities suggest that
there should be observable diversification due to environmental and
spatial processes \citep{wright1943, martiny2006}. Therefore, variation
in microbial community composition seems to result in variation in 
ecosystem function. However, in order for microbial community data to be
useful for ecosystem modeling, the challenge is to identify specifically what variation in community composition
is associated with function across space, time, and environmental gradients.
To accomplish that, we need to separate the close association between environmental variation, community
composition, and ecosystem function to identify the aspects of microbial
biodiversity that are important for ecosystem function.

\subsection*{Extra text for 1.3/1.4}

\begin{enumerate}
    \item Things exhibit population differentiation due to spatial and environmental 
    patterns \citep{wright1943}
    \item Microbes exhibit similar patterns \citep{martiny2006}
    \item Pop gen tries to identify regions of the genome correlated with
    traits
    \item Considering ecosystems as individuals within a population presents
    an analogous problem of determining community markers of ecosystem traits (functions)
    \item Thus the goal of microbial BEF is to identify generalizable patterns
    of genetic variation in microbes to feed into hypothesis testing about
    potential mechanisms or to incorporate into ecosystem models
\end{enumerate}

Typically, microbial community structure-function research questions are framed
as does microbial composition matter to ecosystem function? The answer to this
question is obviously "yes" given that microorganisms mediate many of the
processes of interest. The question then becomes does microbial community
variation within a functional group or overall matter to ecosystem function? 
Generally it is assumed that microbial composition is functionally irrelevant, 
though studies of environmental treatments, common gardens, and reciprocal
transplants have shown that different community compositions are correlated with
different functions. The challenge with these studies is separating the close
connection between environmental variation, community composition, and ecosystem
function. Microorganisms cannot be useful to ecosystem modeling if there
is no identifiable variation in composition that consistently alters function
across space, time, and environmental gradients. The question "do we need to
include microorganisms in ecosystem models?" depends on identifying variation in
the community associated with function independent of the environment. If that's
true, then the next step in understanding or modeling these processes is 
identify what components of the community alter ecosystem function.

There are a number of ways that environmental or spatial covariates could alter
or obscure connections between microbial community structure and ecoystem
function. For example, microbial communities exhibit strong biogeographic
patterns \citep{martiny2006}. The historical effects of geographic proximity,
such as dispersal limitation, could lead to spurious associations between taxa
and function if taxa are unevenly distributed across the functional landscape.
Environmental selection can also shape microbial community structure, so
selection on the microbial community that is independent of the
process could lead to erroneous conclusions about the
underlying drivers of ecosystem function \citep{thompson2017}. For
example, pH is known to regulate both microbial biodiversity patterns
\citep{fierer2006} and methane cycling dynamics \citep{ye2012}, which could lead
to microbial taxa correlated with methane cycling, but mechanistically
unrelated. Environmental factors that directly influence function, such as
moisture, could alter function with or without affecting the community. 
Finally, community stratification where taxa co-occur in certain ecosystems due to
selection or historical effects for reasons unrelated to the ecosystem function
could lead to spurious associations.

\subsection{A new framework for structure-function mapping in microbial
communities}

Microbial ecosystem function could be assessed using statistical techniques
borrowed from quantitative genetics along with the conceptual framework for
community assembly processes provided by metacommunity theory and CAFE. This
would be a two-step process to first identify the portion of variation in
ecosystem function attributable to different aspects of an ecosystem: the
community, the underlying environmental variation, and to spatial processes.

\begin{equation}
V_F=V_E+V_S+V_C+\epsilon
\end{equation}

Ecosystem function is represented by $V_F$, $V_E$ is variation in the
environment and covariation between the community and the environment, $V_S$ is
variation in spatial distance between samples and covariation between the
community and space, and $V_C$ is variation in the community independent of
local selection and historical effects. The parameter $V_C$ also incorporates
unmeasured environmental and spatial effects.

Each of these variance components also correspond to alternative hypotheses for
what drives ecosystem function. If most of the variation in $V_F$ is
attributable to $V_E$, then the environment drives function either directly
(abiotic processes) or indirectly by selecting for a particular microbial
community that maximizes function. In this model, the community is simply a 
conduit through which the environment acts on function. Alternatively, if $V_S$
explains most of the variation in $V_F$ then this suggests that function is
primarily a result of historical contingency and differences in dispersal traits.
Finally, $V_C$ could explain most of the variation in $V_F$. This would be
consistent with reciprocal transplant and common garden experiments showing that
community composition drivers ecosystem function independent of the environment.

This framework allows us to address the following questions: 1. Does variation
in microbial community structure explain a measurable portion of the variation in
ecosystem function or can all of that variation be attributed to the underlying
effect of the environmental and spatial processes? If so, 2. Which members of
the community are significantly correlated with function after controlling for
the covariances of space and environment? Finally, 3. Do these taxa match our hypotheses about
what controls ecosystem function (e.g. functional group abundance) or are there
alternative mechanisms that need to be explored?

\section{Methods}

Sample 16S rRNA gene sequences, environmental covariates, geographic distance,
ecosystem function. Use the DADA2 pipeline to assign ASVs. 
phylogenetic and taxonomic assignment Null
Models \citep{chase2011, stegen2015}

Would it be valuable to use a null model (as in Chase or Stegen) where we
generate random communities based on the distribution across samples and
abundance within samples of each taxon. Then try to correlate those abundances
with our observed rates of ecosystem function to see what distribution of
structure-function correlations to expect given our community data. These sort
of null community generating techniques can omit certain community assembly
processes (such as homogenizing selection or stochastic processes)

An alternative testing approach would be to use Hannah’s permutation test idea
where we randomly permute the process rates ~1000 times and rebuild the model
each time to see what the distribution of significant taxa is.

VC - Correlations between taxa and process determined by accounting for spatial
structure, environmental covariates, and community structure. Represents effect
of taxonomy, unmeasured environmental variables VE - Account for community
structure and correlate environmental variables cov(C, E) - The part of the venn
diagram that disappears when controlling for environment and space VC:VE - Test
the correlations between community and process rate at a variety of
environmental conditions.  epsilon/error term - Effects of natural variation,
unmeasured variables

Another modeling options is HMSC from \cite{ovaskainen2017}

For high-affinity methane oxidation in Gabon: We experimentally controlled some
environmental variables and our measured environmental variables are not
significantly correlated with process rate (C, N, WFPS) Space is correlated with
function

Be careful with attributing a certain \% of the variance to an individual taxa
when performing partial regression on the residuals. If a taxa explains 60\% of
the variance in the residuals after controlling for environment and space that
doesn’t mean it explains 60\% of the overall variance.

\section{Discussion}
Combination of qPCR and pathway partinioing, qSIP \citep{hungate2015},
and NanoSIMS \citep{mayali2012} may allow us to assign portions of
function to particular taxa or functional groups.
Problems that need to be addressed: We shouldn’t assume that functional groups
that putatively perform a process are the rate-limiting step or the strongest
correlate.  There may be unknown members of the community that perform or limit
a process The final step of the process may not be the rate-limiting step: it
may be substrate production or nutrient acquisition or something else (e.g.
Qusheng Jin’s work on modeling methanogenesis) We need to consider the
underlying biogeographic patterns shaping the distribution of microbial
communities (à la GWAS).

\section{Conclusion}

>>>>

@@

Microorganisms mediate many biogeochemical processes and yet the link between
microbial biodiversity and ecosystem function remains unknown. 
Ecologists have investigated the effects of changing
biodiversity on ecosystem function for decades, but this research has primarily
focused on linking terrestrial plant community richness with productivity
\citep{hooper2005}. More recently, there has been an interest in linking
microbial community structure to the functioning of ecosystems both inside and
outside of a host, such as disease states, plant productivity,
and soil greenhouse gas emissions \citep{schimel1998, singh2010}. 
However, it remains unclear to what extent 
microbial community composition is important for determining the rates of ecosystem-scale
functions.  This uncertainty limits our ability to predict and manage host
health and global biogeochemical cycles. To
address this challenge, we propose integrating traditional
biodiversity-ecosystem function research with ideas from genotype-phenotype
mapping in population genetics. This connection will help determine
whether microbial community
composition alters ecosystem-scale function independent
of the underlying environmental variation.

If local selection always optimizes the available biodiversity to maximize
ecosystem function, then microbial community composition should not matter for
predicting the rates of microbially-mediated functions. Instead, 
the rates of these functions should be determined by the
underlying environmental variation. In this case, the microbial community simply
acts as a conduit through which the abiotic
environment alters ecosystem function. However, experiments that manipulate the
connection between environmental factors and microbial community composition
such as environmental treatments, common gardens, and reciprocal transplants
have shown different rates of ecosystem functions for different microbial
communities under the same conditions \citep{reed2007}. 
This has been observed for plant decomposition
\citep{strickland2009}, plant phenology \citep{panke-buisse2015}, soil nitrogen
cycling \citep{balser2005}, and soil greenhouse gas emissions
\citep{cavigelli2000}. Therefore, variation in microbial community composition
seems to generate variation in ecosystem function. However, in order to
incorporate microorganisms into ecosystem models, 
we should distinguish between the portion
of microbial biodiversity that is contributing to ecosystem function as a
consequence of the environmental conditions and that contributing uniquely due to
variation in the community independent of the environment.

Most studies of microbial community function focus on one of two aspects of
microbial community structure that are hypothesized to predict
ecosystem function. The first aspect is functional gene or transcript abundance.
In this case, qPCR or shotgun metagonemic sequencing is used to estimate the
abundance of a gene
or transcript that is a putative marker for a microbial process. For example,
the gene \textit{mcrA}, which encodes the enzyme that performs the final step in
methanogenesis, is hypothesized to predict the rate of
methane production. Other examples include \textit{pmoA} and methanotrophy,
\textit{nifH} and nitrification, and \textit{nosZ} and denitrification. The
rationale for this hypothesis is that the abundance of a functional group (as
inferred from marker gene abundance) should correspond to the rate of the
process performed by that group. There are examples where this relationship
holds \citep{freitag2009, freitag2010, schnyder2018}. However, a review of these
studies found that the abundance of a functional gene or transcript is rarely
correlated with the rate of the corresponding process, with most effects either
negative or not significant \citep{rocca2015}.

The second aspect of microbial community structure hypothesized to predict
ecosystem function is taxonomic or functional
diversity. Diversity is either estimated from sequence variants of a barcode
gene such as the 16S rRNA gene or manipulated through some proxy
of diversity such as sequential dilution or varying filter sizes. Studies that
experimentally manipulate diversity generally find a relationship between
the applied diversity treatment and ecosystem functions including methanotrophy
\citep{schnyder2018}, phosphorus leaching, greenhouse gas emissions
\citep{wagg2014}, and decomposition \citep{maron2018}. However, in each of these
cases, richness is confounded with other factors such as presence or absence of
major phylogenetic groups (nematodes, fungi) or abundance of microbial cells. In
addition, assembled microbial communities pose the same challenges as
macroorganismal diversity experiments, for example lacking replication at the highest
diversity treatment such that that treatment will always have the most
productive taxon. A review of microbial diversity studies shows that
microbial community taxonomic and functional diversity add little variance
explained to models of ecosystem function. Overall, functional gene
abundance and community diversity improve models of ecosystem function less than
one third of the time and increase variance explained by an average of only 8 percentage
points \citep{graham2016}.

These approaches follow on the tradition of macroorganismal
biodiversity-ecosystem function research by measuring or manipulating diversity
and comparing it to function or by looking at the association between richness
or abundance of a functional group (e.g. plants) and the function performed by
that group (e.g. productivity). However, in the case of microbes, our knowledge
of functional groups is quite limited. We cannot be sure that we are accurately
estimating the abundance or diversity of soil microbial functional groups the
way we can plants in a grassland. In addition, we do not know the function of
most microbial taxa and metagenomic sequences recovered from environmental 
samples. Because of this, we should look more
agnostically at the microbial community to identify taxa or groups of taxa that
are important for predicting the rate of ecosystem function. We can accomplish
this by drawing on ideas from population genetics.

The challenge of mapping microbial community structure to ecosystem function is
analogous to the challenge of identifying the genetic basis of complex traits in
organismal populations. In the latter case, a population exhibits variation in a
phenotype (e.g. height or disease state) as well as variation in potentially
thousands of single nucleotide polymorphisms
(SNPs). To identify the genetic basis for a trait, investigators sample from
this population and correlate phenotype with genotype. In most cases, there are
many more loci than individuals and we do not know whether the SNPs are causally
linked or are simply in linkage disequilibrium with a causal mutation. 
Genetic loci identified in these genome-wide association
studies can be the target for future research to dissect the function of those
genes, can be added or removed to test their association with the trait, or can
be used as markers for that disease or phenotype even if it has no known
mechanistic association. This mirrors the problem of microbial
structure-function mapping. In this case, a population of ecosystems exhibit
variation in a particular trait or ecosystem function putatively mediated by
microorganisms as well as variation in metagenomic composition. Investigators
could sample from this population of ecosystems and correlate the rate of an
ecosystem function with microbial community composition or gene composition. 
In order to do this, microbial ecologists should incorporate similar
methodological and statistical approaches as population geneticists in order to
make robust associations between microbes and ecosystem function.

Population geneticists trying to make robust associations between genetic loci
and phenotype must consider several points when designing a genome-wide
association study. First is
to identify the precise trait expected to be influenced by genetic variation. 
Then, to choose a population that exhibits
substantial variation in the trait of interest. This population should also be
otherwise relatively homogeneous to avoid other factors that might influence the
trait. After sampling, statistical methods should take into account population
stratification due to shared ancestry or local selection that can lead to spurious
associations between genes and traits. For example, both human height and
genotype vary systematically across Europe in a latitudinal gradient, which can
lead to spurious genotype-phenotype associations \citep{novembre2008}.

Positive associations between genes and
phenotypes can arise because of true associations, through linkage
disequilibrium with true genes, or through admixture \citep{lander1994}.
Microbial structure-function connections could pose these same problems. There
could be true associations between a microorganism and the ecosystem function
performed by that taxon, or there could be systematic
co-occurrence patterns between one taxon and a causal taxon,
or there could be admixture due to shared history or selection within
a subset of ecosystems. This is true for 16S amplicons and for
genes in metagenomic (or other -omic) datsets. 
Robust structure-function associations rely on
controlling for the underlying geographic and ecological covariance.

Organisms exhibit population differentiation due to geographic and ecological
processes \citep{wright1943}. Neutral processes such as local genetic drift and
reduced gene flow due to geographic separation can lead to population
differentiation. In addition, environmental distance can lead to selection
against migrants \citep{hendry2004} and local selection on endemic populations
to generate variation. Microorganisms also exhibit biogeographic patterns due to
ecological selection and geographic separation \citep{martiny2006}. If dispersal
is non-limiting then the most productive species should always be present and
composition should not matter for local ecosystem function. However, if important
functional groups are dispersal-limited, lost to drift, or are unable to
colonize a site, then there could be important functional consequences of
community differentiation due to geographic or ecological isolation.

@@

Successfully connecting microbial community structure to ecosystem function
depends on being precise about the variation we want to explain. The first and
often overlooked step is choosing a
clearly defined function that exhibits considerable variation across ecosystems. 
Next, be intentional about choosing the
population to be sampled to maximize the amount of variation. For example, how
might ecosystems that are otherwise quite similar vary in function?
Alternatively, how might one ecosystem change in response to a single
environmental change? This could be achieved by sampling across similar ecosystems 
or by imposing experimental conditions that minimize environmental variation or
vary only abiotic factors of interest. 
It is important to take an agnostic approach towards identifying taxa that are
indicators of ecosystem function. It is also important to remember that any
relationships identified in this manner are provisional until further tests are
performed. The work is not done until the organism has been manipulated through
addition, knockout, or variation in abundance.

In this paper we propose integrating microbial biodiversity-ecosystem function
research with ideas and techniques from population genetics to advance our
understanding of the role of microbial commuities in the functioning of
ecosystems. Perhaps the most important part of that discussion is to define the
question carefully. In microbial ecology
structure-function research is focused on answering the question: what is the
unique contribution of the microbial community to ecosystem function? This is of
great interest for two reasons. First, because it addresses what is the singular
contribution of biodiversity to the functioning of ecosystems. Second, on a
practical level, because answering that question will be essential to
incorporate a microbial component into ecosystem models.

Is variation in microbial community
structure associated with differences in ecosystem function across space,
time, and environments?
\section{Methods}

@@

After determining which variance components were significant, we tested the
effect of each ASV on the rate of ecosystem function. We fit a variance
component model for each ASV with ASV abundance as the fixed effect and random
effects for each of the variance components. This tests the relationship between
taxon abundance and the rate of ecosystem function after controlling for
population stratification and data structure. The community similarity matrix
was reconstructed for each model to exclude the predictor ASV. 
Significant ASVs were identified by controlling the false discovery rate using
the \texttt{qvalue} package.

@@

To demonstrate the ideas presented in the Introduction, we re-analyzed data from
a forthcoming publication \citep{meyer2019}. With these data, we demonstrate the
importance of selecting the appropriate population to sample from. We are
precise about the variation we are measuring. Specifically, we measured the rate
of a specific microbial pathway. In order to minimize environmenal variation, we
brought intact soil cores into the lab to incubate them under similar
temperature and methane concentration. We also statistically controlled for
environmental covariates that we couldn't isolate in the lab including soil
carbon and nitrogen, soil bulk density, and soil moisture content. Finally, we
surveyed the microbial community agnostically for microbial markers of ecosystem
function.

We found that for two pathways of methane oxidation in

@@

In this paper, we argue that the traditional approach to microbial BEF research
ignores important understandings about the nature of ecological processes in
determining the distribution of microorganisms. The marker gene hypothesis has
proven unsuccesful in predicting the rates of ecosystem functions from the
abundance of functional genes and in our example study was not significant in one case and
was significant in another, though explained only a small portion of the variation.
Similarly, diversity metrics from the entire Prokrayotic community were not
explanatory. These results agree with recent reviews of this literature and
demonstrate that these approaches are not a fruitful avenue for elucidating
microbial structure-function connections. After identifying significant taxa,
it is notable that none of the significant taxa fall into expected functional
groups. For example, none of the taxa identified in this analysis were
methanotrophs.

Instead, microbial ecologists should treat microbial communities as analogous to
organisms with the metagenome representing the community genome. In this case,
ecosystem function represents a phenotype at the community level. As in
organismal biology, this ecosystem phenotype will be a mix of genotypic effects and
environmental effects. Using this conceptual framework, population genetic
approaches can be applied to microbial community datasets to identify  links
between the composition of microbial communities and the rates of ecosystem
functions.

While this analysis focuses on using genome-wide association studies as a model
for mapping microbial community structure to ecosystem-function, other designs
are possible. For example, artificial ecosystem selection is a viable approach
to enrich for communities with high or low rates of ecosystem function
\citep{swenson2000, panke-buisse2015}. While community-wide association or
ecosystem-wide association or metagenome-wide association or microbiome-wide
association studies have sufficient power to identify taxa that are individually
associated with ecosystem function, whole-community selection could identify
assemblages of organisms with high rates of function that often co-occur in
productive ecosystems.

Another possibility that has not to our knowledge been demonstrated with any
microbial datasets is to apply the ecological form of the Price equation to
estimate the effects of microbial biodiversity on ecosystem function
\citep{fox2006, bannar-martin2018}. Using this equation, a change in ecosystem function between two, matched
observations can be attributed to species additions, species losses, and
changes in abundance of shared species \citep{fox2006,
bannar-martin2018}. To
calculate these vectors, function must be attributed at the species level (e.g.
biomass measurements of individual plant species). To apply this method to
microbial communities we will need to measure ecosystem function on a
per-species basis. There are several ways to do that including quantitative stable-isotope
probing to measure the accumulation of a substrate in the DNA of a portion of
the microbial community \citep{hungate2015}, NanoSIMS to measure the incorporation of nutrients at
the single-cell level \citep{mayali2012}, and isotope source partitioning coupled with measurements
of microbial pathways through quantification of marker genes through qPCR or
metagenomics/metatranscriptomics.

This is novel, because it represent the first time that anyone has treated an
ecosystem like an organism. Further, it is the first time that anyone has
used this GWAS-esque approach while accounting for both environmental and
spatial structure in the data.

@@
